The Astropy Project

### 2017-10-17 main.tex
fix fig captions

\begin{figure}
\includegraphics[width=\textwidth]{coordinates_graph.pdf}
The full graph of possible reference frame transformations implemented in
\texttt{astropy.coordinates}.
\label{fig:frame-transform-graph}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{convolution_example.png}
An example showing different modes of convolution available in the \python ecosystem.  The red x's mark pixels that are set to NaN in the original data (a).  If the data are convolved with a Gaussian kernel on a 9x9 grid using scipy's direct convolution (b), any pixel within range of the original NaN pixels is also set to NaN.  Panel (c) shows what happens if the NaNs are set to zero first: the originally NaN regions are depressed relative to their surroundings.  Finally, panel (d) shows \astropypkg's convolution behavior, where the missing pixels are replaced with values interpolated from their surroundings using the convolution kernel.
\label{fig:convolution-example}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=\textwidth]{coordinates_graph.pdf}
\caption{
    The full graph of possible reference frame transformations implemented in
    \texttt{astropy.coordinates}.
    \label{fig:frame-transform-graph}
}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{convolution_example.png}
\caption{%
    An example showing different modes of convolution available in the \python
    ecosystem.  The red x's mark pixels that are set to NaN in the original data
    (a).  If the data are convolved with a Gaussian kernel on a 9x9 grid using
    scipy's direct convolution (b), any pixel within range of the original NaN
    pixels is also set to NaN.  Panel (c) shows what happens if the NaNs are set
    to zero first: the originally NaN regions are depressed relative to their
    surroundings.  Finally, panel (d) shows \astropypkg's convolution behavior,
    where the missing pixels are replaced with values interpolated from their
    surroundings using the convolution kernel.
    \label{fig:convolution-example}
}
\end{figure}
